Paper Figures and Text

### 2023-02-27 Fish Data Analysis/Paper_Figures.qmd
Paper Graphs and Analysis

```{r}
eight_fish_all_cond <- ggplot(turning_data_sum %>% filter(Type == "Eight Fish"),
       aes(x = Fish_Num_Ratio, y = mean_right_turn, color = Flow))+
  geom_point()+
  geom_line(alpha = 0.25) +
  facet_wrap(~ Darkness + Ablation) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
  scale_colour_manual(values = c(light_ab_color,dark_no_ab_color)) +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))

eight_fish_all_cond_one_chart <- ggplot(turning_data_sum %>% filter(Flow == "Still Water") %>% filter(Type == "Eight Fish"),
                           aes(x = Fish_Num_Ratio, y = mean_right_turn, color = Flow_Ablation_Darkness))+
  geom_point()+
  geom_line(alpha = 0.25) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  #ggtitle("GLM Model of the Probability of a Right Turn in Still Water") +
   ylim(0,1) +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color)) +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))+ 
  labs(color = "Sensory Conditions")

@@

eight_fish_still_model <- ggplot(annushka_turning_data %>% filter(Flow == "Still Water"),
                           aes(x = Fish_Num_Ratio, y = turn_bool, color = Flow_Ablation_Darkness))+
  #geom_jitter(alpha = 0.1, height = 0.025)+
  geom_line(aes(x = Fish_Num_Ratio, y = predict(only_still_model, type="response"), color = Flow_Ablation_Darkness)) +
  geom_point(aes(x = Fish_Num_Ratio, y = predict(only_still_model, type="response"), color = Flow_Ablation_Darkness)) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  #ggtitle("GLM Model of the Probability of a Right Turn in Still Water") +
   ylim(0,1) +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color)) +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))+ 
  labs(color = "Sensory Conditions")

@@

eight_fish_flow_model <- ggplot(annushka_turning_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
                           aes(x = Fish_Num_Ratio, y = turn_bool, color = Flow_Ablation_Darkness))+
  #geom_jitter(alpha = 0.1, height = 0.025)+
  geom_line(aes(x = Fish_Num_Ratio, y = predict(only_flow_model, type="response"), color = Flow_Ablation_Darkness)) +
  geom_point(aes(x = Fish_Num_Ratio, y = predict(only_flow_model, type="response"), color = Flow_Ablation_Darkness)) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  ylim(0,1) +
  #ggtitle("GLM Model of the Probability of a Right Turn in Flowing Water (2 BL/s)") +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color)) +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))+ 
  labs(color = "Sensory Conditions")

eight_fish_all_cond
eight_fish_still_model
eight_fish_flow_model

eight_fish_all_cond_one_chart
```

@@

dark_eight_and_single_graph <- ggplot(dark_eight_and_single_sum,
                           aes(x = Fish_Num_Ratio, y = turn_bool, color = Type))+
  geom_line(aes(x = Fish_Num_Ratio, y = predicted, color = Type)) +
  geom_point(aes(x = Fish_Num_Ratio, y = predicted, color = Type)) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  ylim(0,1) +
  #ggtitle("GLM Model of the Probability of a Right Turn Darkness for Eight or Single Fish") +
  scale_colour_manual(values = c(sim_color,dark_no_ab_color)) +
  #scale_size_continuous(breaks = c(25,50,75)) +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7")) + 
  labs(size = "Number of Turns")

dark_eight_and_single_graph_real <- ggplot(turning_data_sum %>% filter(Flow_Ablation_Darkness == "Still Water, No Ablation, Dark"),
                           aes(x = Fish_Num_Ratio, y = mean_right_turn, color = Type))+
  geom_point()+
  geom_line(alpha = 0.25) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  #ggtitle("GLM Model of the Probability of a Right Turn in Still Water") +
   ylim(0,1) +
  scale_colour_manual(values = c(sim_color,dark_no_ab_color)) +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))+ 
  labs(color = "Sensory Conditions")

@@

ablation_eight_and_single_graph <- ggplot(ablation_eight_and_single_sum,
                           aes(x = Fish_Num_Ratio, y = turn_bool, color = Type))+
  geom_line(aes(x = Fish_Num_Ratio, y = predicted, color = Type)) +
  geom_point(aes(x = Fish_Num_Ratio, y = predicted, color = Type)) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  ylim(0,1) +
  #ggtitle("GLM Model of the Probability of a Right Turn Ablated for Eight or Single Fish") +
  scale_colour_manual(values = c(sim_color,light_ab_color)) +
  #scale_size_continuous(breaks = c(25,50,75)) +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))+ 
  labs(size = "Number of Turns")

@@

light_eight_and_single_graph <- ggplot(light_eight_and_single_sum,
                           aes(x = Fish_Num_Ratio, y = turn_bool, color = Type))+
  geom_line(aes(x = Fish_Num_Ratio, y = predicted, color = Type)) +
  geom_point(aes(x = Fish_Num_Ratio, y = predicted, color = Type)) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  ylim(0,1) +
  #ggtitle("GLM Model of the Probability of a Right Turn Light for Eight or Single Fish") +
  scale_colour_manual(values = c(sim_color,light_no_ab_color)) +
  #scale_size_continuous(breaks = c(25,50,75)) +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))+ 
  labs(size = "Number of Turns")

@@

dark_eight_and_single_graph_real
```

@@

```{r}
turning_mega_plot <- ggarrange(eight_fish_all_cond, eight_fish_still_model, eight_fish_flow_model,
          light_eight_and_single_graph, ablation_eight_and_single_graph, dark_eight_and_single_graph,
          labels = c("A", "B", "C", "D", "E", "F"),
          ncol = 3, nrow = 2)

ggsave("Paper Figures/turning_mega_plot.png", turning_mega_plot, width = 20, height = 12)
```

@@

nnd_still <- ggplot(school_data %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = NND,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = NND_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=NND_Mean_Val-NND_SD_Val, ymax=NND_Mean_Val+NND_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  #ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Still Water") +
  xlab("") +
  ylab("School Height (BL)") +
  theme_light()+ 
  theme(legend.position = "none") +
  #ylim(0,3)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.y = element_text(size = 15))

@@

nnd_flow <- ggplot(school_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = NND,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = NND_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=NND_Mean_Val-NND_SD_Val, ymax=NND_Mean_Val+NND_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  #ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Flow (2 BL/s)") +
  xlab("") +
  ylab("School Height (BL)") +
  theme_light()+ 
  theme(legend.position = "none") +
  #ylim(0,3)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.y = element_text(size = 15))

@@

nnd_glm <- glm(NND ~ Ablation:Darkness:Flow, data = school_data)
emmeans(nnd_glm, specs = pairwise ~ Ablation:Darkness | Flow)

```
### Height Plot

@@

my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"), c("No Ablation, Light", "Ablated, Light"))

@@

height_glm <- glm(School_Height ~ Ablation:Darkness:Flow, data = school_data)
emmeans(height_glm, specs = pairwise ~ Ablation:Darkness | Flow)
```

@@

polar_glm <- glm(School_Polar ~ Ablation:Darkness:Flow, data = school_data)
emmeans(polar_glm, specs = pairwise ~ Ablation:Darkness | Flow)
```

@@

speed_glm <- glm(School_Speed ~ Ablation:Darkness:Flow, data = school_data)
emmeans(speed_glm, specs = pairwise ~ Ablation:Darkness | Flow)
```

@@

area_glm <- glm(Area ~ Ablation:Darkness:Flow, data = school_data)
emmeans(area_glm, specs = pairwise ~ Ablation:Darkness | Flow)
```
### Groups as Mean

mean_group_still <- ggplot(school_data %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = Mean_Groups,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = Mean_Groups_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Mean_Groups_Mean_Val-Mean_Groups_SD_Val, ymax=Mean_Groups_Mean_Val+Mean_Groups_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  #ggtitle("Effect of Available Senses on Speed (BL/s) in Still Water") +
  xlab("") +
  ylab("Mean Number of Groups") +
  theme_light()+ 
  theme(legend.position = "none") +
  #ylim(0,8.5)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.y = element_text(size = 15))

my_comparisons <- list( c("No Ablation, Light", "No Ablation, Dark"), c("No Ablation, Light", "Ablated, Light"))

mean_group_flow <- ggplot(school_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = Mean_Groups,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = Mean_Groups_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=Mean_Groups_Mean_Val-Mean_Groups_SD_Val, ymax=Mean_Groups_Mean_Val+Mean_Groups_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  #ggtitle("Effect of Available Senses on Speed (BL/s) in Still Water") +
  xlab("") +
  ylab("Mean Number of Groups") +
  theme_light()+ 
  theme(legend.position = "none") +
  #ylim(0,8.5)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.y = element_text(size = 15))

mean_group_still
mean_group_flow

@@

group_still <- ggplot(group_sum_data %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "),
           y = count,
           fill = Groups)) + 
    geom_bar(position="fill", stat="identity")+
    xlab("") +
    ylab("Proportion of Time with this Many Groups") +
    theme_light()+ 
    scale_fill_manual(values=c("#1D3557","#325A7C","#457B9D","#7BAFBF","#A8DADC","#D0EBE6","#F1FAEE","#e63946")) +
    theme(axis.text.x = element_text(size = 15),
          axis.text.y = element_text(size = 15),
          axis.title.y = element_text(size = 15))

group_flow <- ggplot(group_sum_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = interaction(Ablation,Darkness,sep=", "),
           y = count,
           fill = Groups)) + 
    geom_bar(position="fill", stat="identity")+
    xlab("") +
    ylab("Proportion of Time with this Many Groups") +
    theme_light()+ 
    scale_fill_manual(values=c("#1D3557","#325A7C","#457B9D","#7BAFBF","#A8DADC","#D0EBE6","#F1FAEE","#e63946")) +
    theme(axis.text.x = element_text(size = 15),
          axis.text.y = element_text(size = 15),
          axis.title.y = element_text(size = 15))

@@

groups_glm <- glm(Groups ~ Ablation:Darkness:Flow, data = school_data)
emmeans(area_glm, specs = pairwise ~ Ablation:Darkness | Flow)

>>>>

```{r}
eight_fish_still <- ggplot(turning_data_sum %>% filter(Type == "Eight Fish") %>% filter(Flow == "Still Water"),
       aes(x = Fish_Num_Ratio, y = mean_right_turn, color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point()+
  #geom_line(alpha = 0.25) +
  geom_smooth(se = F, method = glm, formula = y ~ x, method.args = list(family = "binomial"))+
  #facet_wrap(~ Darkness + Ablation) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  ylim(0,1) +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color)) +
  #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))+ 
  labs(color = "Sensory Conditions")

eight_fish_flow <- ggplot(turning_data_sum %>% filter(Type == "Eight Fish") %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = Fish_Num_Ratio, y = mean_right_turn, color = interaction(Ablation, Darkness, sep =", ")))+
  geom_point()+
  #geom_line(alpha = 0.25) +
  geom_smooth(se = F, method = glm, formula = y ~ x, method.args = list(family = "binomial"))+
  #facet_wrap(~ Darkness + Ablation) +
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  ylim(0,1) +
  scale_colour_manual(values = c(light_no_ab_color,light_ab_color,dark_no_ab_color)) +
  #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))+ 
  labs(color = "Sensory Conditions")

@@

@@

eight_fish_still
eight_fish_flow

turning_glm_still <- glm(turn_bool ~ Fish_Num_Ratio*(Ablation+Darkness),
                         data = annushka_turning_data %>% filter(Flow == "Still Water"), family = binomial)
Anova(turning_glm_still)

turning_glm_flow <- glm(turn_bool ~ Fish_Num_Ratio*(Ablation+Darkness),
                         data = annushka_turning_data %>% filter(Flow == "Flowing Water (2 BL/s)"), family = binomial)
Anova(turning_glm_flow)

@@

dark_eight_and_single_graph <- ggplot(turning_data_sum %>% filter(Flow == "Still Water" & Darkness == "Dark"),
       aes(x = Fish_Num_Ratio, y = mean_right_turn, color = Type))+
  geom_point()+
  geom_smooth(se = F, method = glm, formula = y ~ x, method.args = list(family = "binomial"))+
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  ylim(0,1) +
  scale_colour_manual(values = c(sim_color,dark_no_ab_color)) +
  #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))+ 
  labs(color = "Sensory Conditions")

@@

ablation_eight_and_single_graph <- ggplot(turning_data_sum %>% filter(Flow == "Still Water" & Ablation == "Ablated"),
       aes(x = Fish_Num_Ratio, y = mean_right_turn, color = Type))+
  geom_point()+
  geom_smooth(se = F, method = glm, formula = y ~ x, method.args = list(family = "binomial"))+
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  ylim(0,1) +
  scale_colour_manual(values = c(sim_color,light_ab_color)) +
  #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))+ 
  labs(color = "Sensory Conditions")

@@

light_eight_and_single_graph <- ggplot(turning_data_sum %>% filter(Flow == "Still Water" & Ablation == "No Ablation" & Darkness == "Light"),
       aes(x = Fish_Num_Ratio, y = mean_right_turn, color = Type))+
  geom_point()+
  geom_smooth(se = F, method = glm, formula = y ~ x, method.args = list(family = "binomial"))+
  theme_classic() +
  xlab("# Fish on Left : # Fish on Right") +
  ylab("Probability of a Right Turn") +
  ylim(0,1) +
  scale_colour_manual(values = c(sim_color,light_no_ab_color)) +
  #ggtitle("Observed Probability of a Right Turn Based on Ratio of Fish to the Left and Right") +
  scale_x_continuous(breaks = c(0,0.125,0.25,0.375,
                                0.5,0.625,0.75,0.875),
                     labels = c("7:0","6:1","5:2","4:3",
                                "3:4","2:5","1:6","0:7"))+ 
  labs(color = "Sensory Conditions")

@@

still_light_turning_glm <- glm(turn_bool ~ Fish_Num_Ratio*Type,
                               data = all_turning_data  %>% filter(Flow == "Still Water" & Ablation == "No Ablation" & Darkness == "Light"),
                               family = binomial)
Anova(still_light_turning_glm)

ablated_light_turning_glm <- glm(turn_bool ~ Fish_Num_Ratio*Type,
                               data = all_turning_data  %>% filter(Flow == "Still Water" & Ablation == "Ablated"),
                               family = binomial)
Anova(ablated_light_turning_glm)

dark_light_turning_glm <- glm(turn_bool ~ Fish_Num_Ratio*Type,
                               data = all_turning_data  %>% filter(Flow == "Still Water" & Darkness == "Dark"),
                               family = binomial)
Anova(dark_light_turning_glm)

#Emmeans doesn't quite work since it makes it all into groups and not lines?
real_vs_sim_turning_glm <- glm(turn_bool ~ 0+Fish_Num_Ratio*Ablation*Darkness*Flow*Type, data = all_turning_data, family = binomial)
summary(real_vs_sim_turning_glm)
Anova(real_vs_sim_turning_glm)
emmeans(real_vs_sim_turning_glm, specs = pairwise ~ Type | Flow:Ablation:Darkness)

@@

```{r}
# turning_mega_plot <- ggarrange(eight_fish_still, eight_fish_flow,ggplot() + theme_classic() + theme(axis.line=element_blank()),
#           light_eight_and_single_graph, ablation_eight_and_single_graph, dark_eight_and_single_graph,
#           labels = c("A", "B", "", "C", "D", "E"),
#           ncol = 3, nrow = 2)
# 
# ggsave("Paper Figures/turning_mega_plot.png", turning_mega_plot, width = 20, height = 12)

turning_both_plot <- ggarrange(eight_fish_still, eight_fish_flow,
          labels = c("A", "B"),
          ncol = 2, nrow = 1)

ggsave("Paper Figures/turning_both_plot.png", turning_both_plot, width = 15, height = 7)

turning_single_test_plot <- ggarrange(
          light_eight_and_single_graph, ablation_eight_and_single_graph, dark_eight_and_single_graph,
          labels = c("A", "B", "C"),
          ncol = 3, nrow = 1)

ggsave("Paper Figures/turning_single_test_plot.png", turning_single_test_plot, width = 22, height = 7)

@@

nnd_still <- ggplot(school_data %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = NND,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = NND_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=NND_Mean_Val-NND_SD_Val, ymax=NND_Mean_Val+NND_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  #ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Still Water") +
  xlab("") +
  ylab("School NND (BL)") +
  theme_light()+ 
  theme(legend.position = "none") +
  #ylim(0,3)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.y = element_text(size = 15))

@@

nnd_flow <- ggplot(school_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = interaction(Ablation,Darkness,sep=", "), y = NND,
           color = interaction(Ablation,Darkness,sep=", "),
           fill = interaction(Ablation,Darkness,sep=", ")))+
  stat_dots(side = "both", binwidth = unit(dot_binwidth, "npc")) +
  geom_point(aes(y = NND_Mean_Val), size = 5, color = "Black") +
  geom_errorbar(aes(ymin=NND_Mean_Val-NND_SD_Val, ymax=NND_Mean_Val+NND_SD_Val), width=.2, color = "Black")+
  guides(fill = guide_legend(title = "Condition")) +
  scale_fill_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  scale_color_manual(values=c(light_no_ab_color, light_ab_color, dark_no_ab_color)) +
  #ggtitle("Effect of Available Senses on Nearest Neighbor Distance (NND) in Flow (2 BL/s)") +
  xlab("") +
  ylab("School NND (BL)") +
  theme_light()+ 
  theme(legend.position = "none") +
  #ylim(0,3)+
  stat_compare_means(comparisons = my_comparisons, label = "p.signif", hide.ns = TRUE) +
  theme(axis.text.x = element_text(size = 15),
        axis.text.y = element_text(size = 15),
        axis.title.y = element_text(size = 15))

@@

nnd_glm_still <- glm(NND ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Still Water"))
Anova(nnd_glm_still, test.statistic="F")
length((school_data %>% filter(Flow == "Still Water"))$NND)

nnd_glm_flow <- glm(NND ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
Anova(nnd_glm_flow, test.statistic="F")
length((school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))$NND)

nnd_glm <- glm(NND ~ Ablation*Darkness*Flow, data = school_data)
Anova(nnd_glm)
emmeans(nnd_glm, specs = pairwise ~ Ablation:Darkness | Flow)

### Height Plot

@@

@@

height_glm <- glm(School_Height ~ Ablation*Darkness*Flow, data = school_data)
Anova(height_glm)
emmeans(height_glm, specs = pairwise ~ Ablation:Darkness | Flow)
```

@@

polar_glm <- glm(School_Polar ~ Ablation*Darkness*Flow, data = school_data)
Anova(polar_glm)
emmeans(polar_glm, specs = pairwise ~ Ablation:Darkness | Flow)

polar_glm_still <- glm(School_Polar ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Still Water"))
Anova(polar_glm_still, test.statistic="F")

polar_glm_flow <- glm(School_Polar ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
Anova(polar_glm_flow, test.statistic="F")
```

@@

speed_glm <- glm(School_Speed ~ Ablation*Darkness*Flow, data = school_data)
Anova(speed_glm)
emmeans(speed_glm, specs = pairwise ~ Ablation:Darkness | Flow)

speed_glm_still <- glm(School_Speed ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Still Water"))
Anova(speed_glm_still, test.statistic="F")

speed_glm_flow <- glm(School_Speed ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"))
Anova(speed_glm_flow, test.statistic="F")
```

@@

area_glm <- glm(Area ~ Ablation*Darkness*Flow, data = school_data)
Anova(area_glm)
emmeans(area_glm, specs = pairwise ~ Ablation:Darkness | Flow)
```

@@

group_still <- ggplot(group_sum_data %>% filter(Flow == "Still Water"),
       aes(x = interaction(Ablation,Darkness,sep=", "),
           y = count,
           fill = Groups)) + 
    geom_bar(position="fill", stat="identity")+
    xlab("") +
    ylab("Proportion of Time with this Many Groups") +
    theme_light()+ 
    scale_fill_manual(values=c("8" = "#1D3557","7" = "#325A7C","6" = "#457B9D","5" = "#7BAFBF",
                               "4" = "#A8DADC","3" = "#D0EBE6","2" = "#F1FAEE","1" = "#e63946")) +
    theme(axis.text.x = element_text(size = 15),
          axis.text.y = element_text(size = 15),
          axis.title.y = element_text(size = 15))

group_flow <- ggplot(group_sum_data %>% filter(Flow == "Flowing Water (2 BL/s)"),
       aes(x = interaction(Ablation,Darkness,sep=", "),
           y = count,
           fill = Groups)) + 
    geom_bar(position="fill", stat="identity")+
    xlab("") +
    ylab("Proportion of Time with this Many Groups") +
    theme_light()+ 
    scale_fill_manual(values=c("8" = "#1D3557","7" = "#325A7C","6" = "#457B9D","5" = "#7BAFBF",
                               "4" = "#A8DADC","3" = "#D0EBE6","2" = "#F1FAEE","1" = "#e63946")) +
    theme(axis.text.x = element_text(size = 15),
          axis.text.y = element_text(size = 15),
          axis.title.y = element_text(size = 15))

@@

groups_glm <- glm(Groups ~ Ablation*Darkness*Flow, data = school_data, family  = poisson)
Anova(area_glm)
emmeans(area_glm, specs = pairwise ~ Ablation:Darkness | Flow)

groups_glm_still <- glm(Groups ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Still Water"), family  = poisson)
Anova(groups_glm_still, test.statistic="F")

groups_glm_flow <- glm(Groups ~ Ablation*Darkness, data = school_data %>% filter(Flow == "Flowing Water (2 BL/s)"), family  = poisson)
Anova(groups_glm_flow, test.statistic="F")
